From Reversible Programs to \\ Univalent Universes and Back

### 2017-06-30 upi.tex
move wavefront to end of section 3 introction by fleshing out the vacuous example, and add the example with only a single inhabitant.

@@

An example of a univalent fibration is $P : \mathbb{2} \rightarrow \mathbb{U}$
defined as $P(\fc) = \mathbb{0}$ and $P(\tc) = \mathbb{1}$ illustrated below:

\medskip\noindent In this case, the space of equivalences
$P(\fc) = \mathbb{0} \simeq \mathbb{1} = P(\tc)$ is empty and so is the space of
paths $\fc \equiv \tc$ and hence these two spaces are vacuously equivalent.

>>>>

On the other hand, for $P : \mathbb{2} \rightarrow \mathbb{U}$
defined as $P(\fc) = \mathbb{0}$ and $P(\tc) = \mathbb{1}$, we do
obtain a univalent fibration.

\medskip\noindent In this case, the space of equivalences
$\mathbb{0} \simeq \mathbb{1}$ is empty, as is the space of
paths $\fc \equiv \tc$. These two are thus vacuously equivalent.

Of course, we can obtain another (trivial) example from $\mathbb{1}$:
$P : \mathbb{1} \rightarrow \mathbb{U}$, defined as
$P(\star) = \mathbb{1}$. $P$ is univalent as both $\star \equiv \star$ and
$\mathbb{1} \simeq \mathbb{1}$ each have a single inhabitant.

@@
